\chapter*{Abstract}

The traditional ticketing industry faces challenges such as ticket scalping, fraud, and limited transparency in secondary markets. Blockchain technology has the potential to revolutionize ticketing by offering a secure, transparent, and efficient solution. This thesis proposes a blockchain-based ticketing system that leverages the core strengths of blockchain technology to address these shortcomings.

The system utilizes smart contracts to manage the ticket lifecycle securely, from creation by event organizers to purchase and transfer by users. This ensures authenticity and eliminates the risk of counterfeiting. Additionally, the system facilitates a secure and transparent secondary market for ticket resale, with fair pricing mechanisms and clear ownership tracking.

Keywords: Blockchain, Ticketing System, NFTs

\chapter*{Resumo}

A indústria tradicional de bilhetes enfrenta desafios como a revenda ilegal de bilhetes, fraude e transparência limitada nos mercados secundários. A tecnologia blockchain tem o potencial de revolucionar o setor de bilheteiras ao oferecer uma solução segura, transparente e eficiente. Esta tese propõe um sistema de bilheteira baseado em blockchain que aproveita as principais capacidades desta tecnologia para resolver esses problemas.

O sistema utiliza \textit[smart contracts] para gerir de forma segura o ciclo de vida dos bilhetes, desde a criação pelos organizadores de eventos até à compra e transferência pelos utilizadores. Isto garante a autenticidade e elimina o risco de falsificação. Além disso, o sistema facilita um mercado secundário seguro e transparente para a revenda de bilhetes, com mecanismos de preços justos e um rastreio claro de propriedade.

Palavras-chave: Blockchain, Sistema de Bilheteira, NFTs