\section{Related Work}
\label{sec:related_work}

In this section, we explore some of the most prominent traditional ticket-selling platforms and their functionalities. Additionally, we discuss the application of NFTs (Non-Fungible Tokens) in industries such as art and gaming, highlighting key projects and trends.

\subsection{Traditional Ticket-Selling Platforms}
\label{subsec:traditional_ticket_selling_platforms}

Several traditional platforms are widely used for ticket sales today. \href{https://ticketline.sapo.pt/}{Ticketline} and \href{https://blueticket.meo.pt/}{Blueticket} are two of the largest and most reputable Portuguese companies specializing in ticket sales for a variety of events, including concerts, sports matches, theater performances, and exhibitions. These platforms also collaborate with physical retailers, such as \href{https://www.worten.pt/}{Worten}, \href{https://www.fnac.pt/}{Fnac}, and \href{https://www.elcorteingles.pt/}{El Corte Inglés}, offering users the convenience of purchasing tickets in person.

Both platforms maintain comprehensive websites where event organizers can list their events. Users can browse events, view detailed information, and purchase tickets online. Options are available to either print the tickets at home or collect them at physical outlets.

% Comparison table between traditional ticket-selling platforms and Ticketchain to be added here.

\subsection{Application of NFTs}
\label{subsec:application_of_nfts}

NFTs have seen widespread adoption in industries like art and gaming, where they are used to represent ownership of unique digital assets. In the art industry, NFTs are employed to create and sell digital artworks, which are authenticated on the blockchain to ensure uniqueness. These digital pieces can be traded or sold, with creators often benefiting from resale royalties. 

In the gaming industry, NFTs are used to represent unique in-game items, such as skins, weapons, or characters, that can be bought, sold, and traded between players. These items can enhance gameplay or serve as collectibles. One of the most famous NFT projects is the \href{https://www.boredapeyachtclub.com/}{Bored Ape Yacht Club}, which features a collection of digital apes (in JPEG format) that have sold for millions of dollars. Beyond just being digital art, ownership of these NFTs grants access to exclusive events, merchandise, and a vibrant community of collectors.
